An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-24 paper/paper.tex
Work on the churn test section in the methodology

% These are necessary to compile
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{amsmath}

% Don't know which ones of these we actually use
%%\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{alltt}
\usepackage{color}
\usepackage{fancyvrb}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{verbatim}
%\usepackage[autostyle]{csquotes}
%\usepackage[toc,page]{appendix}

% Setting the page alignment with this package
\usepackage[top=1in, bottom=1.5in, left=1.5in,right=1.5in]{geometry}

@@

% TODO make title page look nicer
\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO maybe nice pic? \includegraphics [width = 0.3\textwidth] {images/wpilogo}\\[0.3cm]
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[0.7cm]
\LARGE{\textsc {\textbf{An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems}}}\\[0.5cm]
\vspace{0.2cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.5cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{0.5cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

Although they have not gained much popularity, peer to peer (P2P) file backup systems have been created and studied by researchers for over a decade. These systems do not suffer from the aforementioned drawbacks of centralized systems; they are free to use, limited in storage only by the user, and do not require a trusted central entity. Instead of backing up their data to a server, peers back up their data to \textit{each other}. However, abandoning the centralized server model in favor of a distributed one brings with it new problems that must be addressed before wide-spread adoption can be expected. Research in this area has focused on topics such as handling node churn, moving towards a completely decentralized system, efficient routing algorithms, and minimizing bandwidth.
% TODO citations for each research topic

@@

We have designed and implemented a new P2P backup system, called BTBackup, that improves the speed of backing up and recovering data. Our main contribution, and the technology responsible for faster file backup and recovery, is the way in which we handle data transfer: BitTorrent Sync, a new synchronization application created by BitTorrent, Inc. BitTorrent Sync uses a modified version of the BitTorrent protocol in order to quickly synchronize files between groups of peers. This protocol is especially effective at transferring large files, which makes its use perfect for the domain of P2P file backup. By leveraging BitTorrent Sync, we take advantage of BitTorrent's ability to better utilize a peer's bandwidth by downloading from multiple sources at once. This is in contrast to other P2P backup systems, which directly download from one source at a time. Our approach takes advantage of the fact that P2P backup systems require data replication, the act of inserting several redundant copies of data into the network, to combat node churn. We view the the set of nodes storing replications for a given file as a BitTorrent swarm, allowing us to apply the BitTorrent protocol without additional overhead.

@@

In this chapter, we discuss the design of BTBackup, our Peer to Peer backup system. See Chapter \ref{chap:impl} for our implementation of it.

@@

PeerStore showed that separating the metadata layer from the data layer can result in significant bandwidth reduction. By relaxing the requirement to strictly maintain a set number of replicas per file, the system can reduce the data migration cost. For example, it is unnecessary to \textit{immediately} find a new replication node when a current replication node goes offline; only when the node has shown to be consistently unavailable should the system seek a replacement. Given that there exists more than one replica of a peer's data, having one temporarily offline is not catastrophic.\footnote{Note that this implies the low possibility of not being able to recover data that is backed up. Also note that this situation is unavoidable in \textbf{all} backup systems. We leverage this fact by relaxing the aforementioned requirement like PeerStore; this sacrifices theoretical availability for performance and usability. See Section \ref{subsec:TheMetadataLayer_sec:SystemDesign} for the discussion of the parameterization of these variables in our implementation. See Section \ref{} for our methodology of testing the parameter. Finally, see Section \ref{} for a comparison of the results of different values for the parameter.}
% TODO add references once we know section names

@@

In the broadest sense, the metadata layer is used by peers to find nodes. Peers use it to determine which nodes will be used to store their data, and, in the event of local data loss, peers use it to find those same nodes so they can recover their data. The former is described below in \textbf{Finding Replication Nodes}, the latter in \textbf{Metadata Record}.
% TODO don't hardcode these

@@

\subsubsection{Finding Replication Nodes} \label{subsubsec:FindingReplicationNodes}

@@

Our main contribution in this paper, and the only requirement of the data layer, is that it uses BitTorrent as the data transport protocol. By doing so we increase the speed of data recovery, because the peer can download the data from all replication nodes simultaneously, and data backup, because the nodes, in addition to the peer, can give the data they possess to each other.

@@

Furthermore, all communication between peers and nodes is encrypted to limit information leakage.

@@

For users of our system to take advantage of the speed increases offered by the BitTorrent protocol, a sufficient number of replicas need to be maintained in the overlay network (for a comprehensive explanation of how the BitTorrent protocol works, see Section \ref{sec:TheBitTorrentProtocol}). Since the P2P network will be composed of ordinary network users, backups that are created may not always be available. Therefore, it is not enough to rely on the backups that are created when a file is first backed up; in the worst-case scenario, all of the nodes on which a user has created replicas have permanently left the network, leaving the user with no way to retrieve any backup. If one or two replication nodes are online when the backups are needed, the user will be able to recover their file but will not see much of a speed benefit from the BitTorrent protocol, as opposed to when all replication nodes are online.

@@

\section{Fairness} \label{sec:Fairness}
% TODO we say "if n backups", but also refer to each backup as a "replica". we should be consistent. where else do we do this? ctrl-f replica
To ensure fairness (see Section \ref{sec:BackgroundFairness} for background information), each node must contribute storage space proportional to the amount that they are backing up. Since a peer will have replicas of its file stored on multiple nodes, the amount of space that a peer offers\footnote{That is, offers to store when it assumes the role of a node.} must be much larger than the amount of unique data that it is backing up. If $n$ backups are maintained for each file and $\mathcal{F}$ represents the set of files that a peer backs up, the total amount of space $t$ that the peer must offer can be expressed as:
\begin{equation}
t=n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i)
\end{equation}
There exists one problem with this mechanism: when the network first starts up, no peer has created any backups, so no one is obligated to store data for other peers. To solve this, our system requires that each peer is obligated to take at least $s$ bytes of data from other peers, regardless of how much data it has backed up. To include this, $t$ can be reexpressed as:
\begin{equation}
t=max(s,n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i))
\end{equation}
Let $a$ be the amount of data a node is currently storing, and $z$ be the size of a file a peer is trying to back up. When the peer finds a candidate node with $t - a > z$, it can choose that node as a replication site, knowing that it is obligated to accept the data.

\subsection{Challenge Mechanism} \label{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup}
Even though the technique described above allows peers to find nodes with a sufficient amount of storage space, it does not guarantee that the node will keep its promise and actually store the data. For instance, a node can accept a peer's data, only to discard it immediately. A peer will only find out that its data has been discarded when it needs to retrieve backups, at which point it is too late.

@@

\section{System Design}
\subsection{Overview} \label{subsec:Overview_sec:SystemDesign_chap:Implementation}

We have designed our system to be modular. We realize that future work on our system might include the replacement of our data and metadata layers. Our solution for making these parts interchangeable with different implementations is to define standard interfaces between the two layers and the core application. These interfaces can be followed to create new implementations for the two layers. Along with these two layers, there is one more major part to our application: the system core. The system core comprises the core functionality of our system, which includes accepting and executing user commands, receiving network requests from other peers, and maintaining the P2P system.

@@

\subsubsection{Console Controller}
%Takes user input
%the reader can think about this as the ``client'' part of the peer
%Spawns all other controllers
The main purpose of the Console Controller is to allow input to our program from a text console. During runtime, it waits for the user to enter a command, determines which command was entered and with what parameters when applicable, and calls the appropriate function to handle the command. It acts as the main thread of execution in our program. Currently, there are only two commands that are supported via this controller:
\begin{itemize}
\item backup  $<$fileName$>$ - adds a file to backup.
\item rm $<$fileName$>$ - removes a file that is already being backed up.
\end{itemize}
% TODO implement rm command (just send UpdateFileSize(0))

Since the Console Controller runs on the main thread of execution, it manages the life cycle of the other controllers.

@@

As we have already discussed, churn is important to consider when designing a realistic P2P backup system. In this test scenario, we measured how well our system handles different levels of churn. To do this, we created a network of 100 peers, in addition to the tracker and the log server. Each peer had a single 1GB file that it tried to back up. This means that, with five replicas per file, there was 600GB of data in the network.

% TODO: When we pick the actual distribution functions, write them in this paragraph.
To create churn, we have peers enter and leave the network at varying time intervals. Running our program signifies when a peer enters the network, while exiting our program signifies leaving the network. Both of these were controlled by a script that we wrote. To determine the duration of time, the script picked a timeout from one of two exponential distributions, depending on whether the peer was entering or leaving the network. This is the strategy used in the experimental results of PeerStore \cite{PeerStore}. By using an exponential distribution, there will be a greater chance of peers going offline for a short amount of time. This is useful, since in a production environment, many nodes will go offline for a short amount of time (i.e. users shutting their machine down at night), but fewer will stay offline for a long period of time or permanently leave the network.

@@

As it stands now, our system is unusable by a majority of Internet users, since they live behind routers with NAT. We need to design some mechanism to overcome this in our system. We can turn to Skype, BitTorrent, BitTorrent Sync, and other P2P applications for inspiration.

% TODO explain what NAT is why and it makes P2P hard?

\subsection{Finding the optimal number of replications}

In order to minimize storage overhead, we would like to find the optimal number of data replicas to create before their provided speed enhancement is outweighed by their storage cost.

Our approach takes advantage of the need for replicas in a P2P backup system to combat node churn; we use the already-present replication nodes as a BitTorrent swarm, which provides the speed boost without additional overhead. However, we wonder if the cost of creating replicas in addition to the ones needed for data availability would improve the data transfer rate even more. The fact that the additional replicas also provide greater data availability should also be taken into account.

@@

There are many features missing from our implementation that we would like to see added. A brief, nonexhaustive list follows. It does not include other future work detailed in this chapter.

\begin{enumerate}
    \item Replace the centralized tracker with a DHT to become completely decentralized.
    \item Encrypted communication between peers to reduce information leakage.
    \item The ability to backup folders, not just files.
\end{enumerate}

>>>>

%%\usepackage{setspace}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{enumerate}
\usepackage{mathrsfs}
\usepackage{alltt}
\usepackage{color}
\usepackage{fancyvrb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{verbatim}
\usepackage{hyperref}
%\usepackage[autostyle]{csquotes}
%\usepackage[toc,page]{appendix}

\usepackage[top=1in, bottom=1.5in, left=1.5in,right=1.5in]{geometry} % setting the page alignment with this package

@@

\begin{titlepage}
\begin{center}
\thispagestyle{empty}
% TODO maybe nice pic? \includegraphics [width = 0.3\textwidth] {images/wpilogo}\\[0.3cm]
% TODO install \textsc font
\Large{\textbf{A Major Qualifying Project Report\\ \large{ON}}}\\[0.7cm]
\LARGE{\textsc {\textbf{An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems}}}\\[0.5cm]
\vspace{0.2cm}
\Large{\textbf{\\Submitted to the Faculty of }}
\LARGE{\textbf{\\WORCESTER POLYTECHNIC INSTITUTE\\}}
\vspace{0.5cm}
\Large{\textbf{\\In Partial Fulfillment of the Requirement for the}}
\Large{\textbf{\\Degree of Bachelor of Science}}
\vspace{0.5cm}
\Large{\textbf{\\by}}\\[0.5cm]
\large{\textbf{Dan Bouffard}}\\
\large{\textbf{Marc Green}}\\
\vspace{0.5cm}
\large{\textbf{UNDER THE GUIDANCE OF}}\\
\large{\textbf{Professor G\'abor N. S\'ark\"ozy}}\\
\vspace{1cm}
\large{\textbf{\\May 1, 2014}}\\
\end{center}
\end{titlepage}

@@

Although they have not gained much popularity, peer to peer (P2P) file backup systems have been created and studied by researchers for over a decade. These systems do not suffer from the aforementioned drawbacks of centralized systems; they are free to use, limited in storage only by the user, and do not require a trusted central entity. Instead of backing up their data to a server, peers back up their data to \textit{each other}. Research in this area has focused on topics such as handling node churn, moving towards a completely decentralized system, efficient routing algorithms, and minimizing bandwidth.
% TODO citations for each research topic

@@

We have designed and implemented a new P2P backup system that improves the speed of backing up and recovering data. Our main contribution, and the technology responsible for faster file backup and recovery, is the way in which we handle data transfer: BitTorrent Sync, a new synchronization application created by BitTorrent, Inc. BitTorrent Sync uses a modified version of the BitTorrent protocol in order to quickly synchronize files between groups of peers. This protocol is especially effective at transferring large files, which makes its use perfect for the domain of P2P file backup. By leveraging BitTorrent Sync, we take advantage of BitTorrent's ability to better utilize a peer's bandwidth by downloading from multiple sources at once. This is in contrast to other P2P backup systems, which directly download from one source at a time.

@@

In this chapter, we discuss the design of our Peer to Peer backup system. See Chapter \ref{chap:impl} for our implementation of it.

@@

PeerStore showed that separating the metadata layer from the data layer can result in significant bandwidth reduction. By relaxing the requirement to strictly maintain a set number of replicas per file, the system can reduce the data migration cost. For example, it is unnecessary to immediately find a new replication node when a current replication node goes offline; only when the node has shown to be consistently unavailable should the system seek a replacement. Given that there exists more than one replica of a peer's data, having one temporarily offline is not catastrophic.\footnote{Note that this implies the low possibility of not being able to recover data that is backed up. Note that this situation is unavoidable in \textbf{all} backup systems. By relaxing the aforementioned requirement like PeerStore, we leverage this fact by sacrificing theoretical availability for performance and usability. See Section \ref{subsec:TheMetadataLayer_sec:SystemDesign} for the discussion of the parameterization of these variables in our implementation. See Section \ref{} for our methodology of testing the parameter. Finally, see Section \ref{} for a comparison of the results of different values for the parameter.}
% TODO add references once we know section names

@@

In the broadest sense, the metadata layer is used by peers to find nodes. Peers use it to determine which nodes will be used to store their data, and, in the event of local data loss, peers use it to find those same nodes so they can recover their data. The former is described below in \textbf{Finding Replicant Nodes}, the latter in \textbf{Metadata Record}.
% TODO don't hardcode these

@@

\subsubsection{Finding Replicant Nodes} \label{subsubsec:FindingReplicantNodes}

@@

Our main contribution in this paper, and the only requirement of the data layer, is that it uses BitTorrent as the data transport protocol. By doing so we increase the speed of data recovery, because the peer can download the data from all replication nodes simultaneously.

@@

% TODO note that this isn't done in the impl
Furthermore, all communication between peers and nodes is encrypted to limit information leakage.

@@

%If less than X number of replicas, a peer should make a new replica on a node that has yet to hold a replica. (is this a TODO?)
For users of our system to take advantage of the speed increases offered by the BitTorrent protocol, a sufficient number of replicas need to be maintained in the overlay network (for a comprehensive explanation of how the BitTorrent protocol works, see Section \ref{sec:TheBitTorrentProtocol}). Since the P2P network will be composed of ordinary network users, backups that are created may not always be available. Therefore, it is not enough to rely on the backups that are created when a file is first backed up; in the worst-case scenario, all of the nodes on which a user has created replicas have permanently left the network, leaving the user with no way to retrieve any backup. If one or two replication nodes are online when the backups are needed, the user will be able to recover their file but will not see much of a speed benefit from the BitTorrent protocol, as opposed to when all replication nodes are online.

@@

\section{Fairness} \label{sec:Fairness}
% People store proportional amount of data compared to how much they are backing up
% TODO we say "if n backups", but also refer to each backup as a "replica". we should be consistent. where else do we do this? ctrl-f replica
To ensure fairness (see Section \ref{sec:BackgroundFairness} for background information), each node must contribute storage space proportional to the amount that they are backing up. Since a peer will have replicas of its file stored on multiple nodes, the amount of space that a peer offers\footnote{That is, offers to store when it assumes the role of a node.} must be much larger than the amount of unique data that it is backing up. If $n$ backups are maintained for each file and $\mathcal{F}$ represents the set of files that a peer backs up, the total amount of space $t$ that the peer must offer can be expressed as:
\begin{equation}
t=n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i)
\end{equation}
There exists one problem with this mechanism: when the network first starts up, no peer has created any backups, so no one is obligated to store data for other peers. To solve this, our system requires that each peer is obligated to take at least $s$ bytes of data from other peers, regardless of how much data it has backed up. To include this, $t$ can be reexpressed as:
\begin{equation}
t=max(s,n\sum\limits_{i=1}^{|\mathcal{F}|} size(F_i))
\end{equation}
Let $a$ be the amount of data a node is currently storing, and $z$ be the size of a file a peer is trying to back up. When the peer finds a candidate node with $t - a > z$, it can choose that node as a replication site, knowing that it is obligated to accept the data.

\subsection{Challenge Mechanism} \label{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup}
% TODO: Fix this section so that it talks about the new challenge mechanism.
Even though the technique described above allows peers to find nodes with a sufficient amount of storage space, it does not guarantee that the node will keep its promise and actually store the data. For instance, a node can accept a peer's data, only to discard it immediately. A peer will only find out that its data has been discarded when it needs to retrieve backups, at which point it is too late.

@@

\section{System Design}
\subsection{Overview} \label{subsec:Overview_sec:SystemDesign_chap:Implementation}
%Diagram of system design
We have designed our system to be modular. We realize that future work on our system might include the replacement of our data and metadata layers. Our solution for making these parts interchangeable with different implementations is to define standard interfaces between the two layers and the core application. These interfaces can be followed to create new implementations for the two layers. Along with these two layers, there is one more major part to our application: the system core. The system core comprises the core functionality of our system, which includes accepting and executing user commands, receiving network requests from other peers, and maintaining the P2P system.

@@

\subsubsection{Console Controller}
%Takes user input
%the reader can think about this as the ``client'' part of the peer
%Spawns all other controllers
The main purpose of the Console Controller is to allow input to our program from a text console. During runtime, it waits for the user to enter a command, determines which command was entered and with what parameters when applicable, and calls the appropriate function to handle the command. It acts as the main thread of execution in our program. Currently, there are only two commands that are supported via this controller:
\begin{itemize}
\item backup  $<$fileName$>$ - adds a file to backup.
\item rm $<$fileName$>$ - removes a file that is already being backed up.
\end{itemize}
Since the Console Controller runs on the main thread of execution, it manages the life cycle of the other controllers.

@@

As we have already discussed, churn is important to consider when designing a realistic P2P backup system. The goal of this test scenario is to determine how well our system handles churn. To do this, we created a network of 100 peers, in addition to the tracker and the log server. Each peer had a single 100MB file that it tried to back up. This means that, with five replicas per file, there was 6GB of data in the network, 5GB of which were replica files.

We measure the effects of churn by logging the number of bytes sent over the network throughout each instance. We gathered this data by using the \textit{ifconfig} command, which reports the total number of bytes that have been sent and received on each interface. For this scenario, we only collected the number of bytes sent by each peer, as the number of bytes received does not take packets lost in the network into consideration. The exact command used is as follows:

\begin{verbatim}
ifconfig eth0 | grep 'TX bytes' | awk -F : '{print $3}' | \
  awk '{print $1}'
\end{verbatim}

where \textit{eth0} is the name of the network interface. With the ability to query this at any time, we were able to determine the number of bytes sent each second by calling the above command once every second. The output is then sent to a logging server, which collects the data from every peer into one log file.

There are two instances within this test scenario. The first is our control, where all peers joined the network at the start and did not leave until the end of the instance. Running this test allowed us to see how much data is transferred without any churn. In the second instance, nodes enter and leave the network at a rate specified by the distribution function described below. % Pickup here

% TODO: Make sure this is very understandable.
In our tests, we modeled a network where each peer had an average uptime of 150 seconds (2.5 minutes) and an average downtime of 75 seconds (1.25 minutes). We chose these numbers based on the amount of time a typical user might be online in a given day. We reasoned that, if a typical user keeps his or her computer on during the day and shuts it off when he or she sleeps (for 8 hours), then the uptime in the average day will be 16 hours. As explained in section \ref{subsec:ChallengeMechanism_sec:Fairness_chap:BTBackup}, our challenging mechanism sends a challenge message to backup nodes every 6 hours and blacklists them upon 50\% challenge failure over 4 days, meaning that a node is blacklisted if they fail 8 or more tests. We scaled these numbers down so that we would have a 1 hour test (a factor of 360): a 6 hour challenge becomes a 60 second challenge, and the challenge period becomes 16 minutes. To make the challenge period evenly fit into the 1 hour test, we rounded the challenge period down to 15 minutes, making the scaling a factor of 384. From this factor, we scale 16 hours and 8 hours down to 2.5 minutes and 1.25 minutes, respectively.

To create churn, we have peers enter and leave the network at varying time intervals. The tests were controlled by a Python script that initialized the test environment and ran the test upon machine boot. The script start and stops BTBackup to simulate the node entering and leaving the network, respectively. To determine the duration of time, the script picked a timeout from one of two distributions, depending on whether the peer was entering or leaving the network. This is the strategy used in the experimental results of PeerStore \cite{PeerStore}.

Our distributions are a combination of three functions over the range $[0,1)$. In order to choose an uptime or downtime, a node chooses a random number in this range, and applies it to the following multipart function:

$$
f(x)=
\begin{cases}
10xc & \mbox{ if $0 \leq x < 0.2$ } \\
[4(x-0.2)+2]c & \mbox{ if $0.2 \leq x < 0.8$ } \\
[e^{21(x-0.84)}+3.5]c & \mbox{ if $0.8 \leq x < 1$ }
\end{cases}
$$

% TODO: Is it accurate to say that the multipart function is continuous?
The value of $c$ is what differentiates between choosing an uptime or a downtime. In order to obtain the average uptime and downtime stated above, we used $c=50$ for uptime and $c=25$ for downtime. Since the middle equation is our biggest range, we modeled it so that its average values for each value of $c$ approximately corresponds to the average uptime and downtime. We used a steeper linear equation from 0 to 0.2 so that very short uptimes and downtimes are represented, but very few nodes will ever choose values using this function. The steepness also makes the transition to the middle equation quick but continuous. For the top range, we chose an exponential function so very long uptimes and downtimes are represented. For example, the upper bound for uptime is 3509.32 seconds, or 58.49 minutes for $c=50$, which is almost the entire length of the test. Nodes who pick these values represent computers that are almost always online, such as servers or NAS units.

%By using an exponential distribution, there will be a greater chance of peers going offline for a short amount of time. This is useful, since in a production environment, many nodes will go offline for a short amount of time (i.e. users shutting their machine down at night), but fewer will stay offline for a long period of time or permanently leave the network.

@@

As it stands now, our system is unusable by a majority of Internet users, since they live behind routers with NAT. We need to implement some mechanism to bypass this. We can turn to Skype, BitTorrent, BitTorrent Sync, and other P2P applications for inspiration.

@@

There are many features missing from our implementation that we would like to see added. A brief, nonexhaustive list follows. It do not include features also missing from the specification.

\begin{enumerate}
    \item Replace the centralized tracker with a DHT
    \item Encrypted communication between peers to reduce information leakage
    \item The ability to backup folders, not just files
\end{enumerate}
